Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-08 draft.tex
modify proof of lemma 2 to take account of war possibility

Given that the continuation value from Status Quo is higher than both that from playing Cede and Fight, player $s$ will play Status Quo. The argument for player $g$ is symmetric. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 2} \\
In the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is reunification, payoffs in this absorbing state in the period in which the investment is made are $U_p^{t,RU}= -\alpha -R_p^{RU}$ and $U_c^{t,RU}= \beta -R_c^{RU}$ where $SQ$ and $RU$ distinguish investments under the status quo and reunification scenarios respectively.

@@

Since the patron is willing to invest up to $\frac{\alpha}{1 -\de}$, $\frac{\beta}{1 -\de} + \mu \leq \frac{\alpha}{1 -\de}$ is a sufficient condition to prevent $c$ from inducing the \emph{reunification} outcome. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 3} \\
Again, in the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is recognition of the secessionists, per-period payoffs in this absorbing state become $U_p^{t,REC}= \lambda -R_p^{REC}$ and $U_c^{t,REC}= -\nu -R_c^{REC}$ where $SQ$ and $REC$ distinguish investments under the status quo and recognition scenarios respectively.

>>>>

Given that the continuation value from Status Quo is higher than both that from playing Cede and Fight, player $s$ will play Status Quo. The argument for player $g$ is symmetric. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 2} \\
Begin by assuming Restriction \ref{res:new}a holds. In the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is reunification, payoffs in this absorbing state in the period in which the investment is made are $U_p^{t,RU}= -\alpha -R_p^{RU}$ and $U_c^{t,RU}= \beta -R_c^{RU}$ where $SQ$ and $RU$ distinguish investments under the status quo and reunification scenarios respectively.

@@

Since the patron is willing to invest up to $\frac{\alpha}{1 -\de}$, $\frac{\beta}{1 -\de} + \mu \leq \frac{\alpha}{1 -\de}$ is a sufficient condition to prevent $c$ from inducing the \emph{reunification} outcome.

If Restriction \ref{res:new}a is violated, as the secessionists' status quo payoffs degrade from period to period, they will fall below $\omega_s^t$ before they fall below $L_s^t$. If no investment is made in $Q_s^{t-1}$, the secessionists will choose the war outcome. Restriction \ref{res:new}b guarantees that the patron will make the investment $R_p^{t'}  = \omega_s^{t-1} -\mu - Q_s^{t-1} \leq \mu$ to prevent the secessionists choosing war since this $R_p^{t'}$ is strictly less than the patron's expected loss from the war outcome. Note that the patron's actual investment will be the maximum of the investment required to prevent the war and ceding outcomes. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 3} \\
Again, in the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is recognition of the secessionists, per-period payoffs in this absorbing state become $U_p^{t,REC}= \lambda -R_p^{REC}$ and $U_c^{t,REC}= -\nu -R_c^{REC}$ where $SQ$ and $REC$ distinguish investments under the status quo and recognition scenarios respectively.
